How cryptic is cryptic diversity? Machine learning approaches to classifying morphological variation in \textit{Emys marmorata} (Testudinoidea, Emydidae).

### 2014-12-03 doc/draft_turtle.tex
miss classification tables

@@

\begin{figure}[ht]
  \centering
  \includegraphics[height = \textheight, width = \textwidth, keepaspectratio = true]{figure/sel_val}
  \caption{CAPTION}
  \label{fig:sel}
\end{figure}

>>>>

 % i have three tables for this. need to find a nice way of displaying these. also they require large amounts of edits
\begin{table}
  \begin{scriptsize}
    \include{rf_miss}

    \include{mm_miss}

    \include{ll_miss}
  \end{scriptsize}
  \caption{Results of comparisons between correctly and incorrectly classified observations from the testing data set. For each scheme, the classifications with at least 10 observations were tested. This was done for each of the three modeling techniques included in this study.}
  \label{tab:miss_tests}
\end{table}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[height = \textheight, width = \textwidth, keepaspectratio = true]{figure/sel_val}
  \caption{Graphical representation of the AICc and AUC values from model selection for multinomial logigistic regression and linear discriminate analysis, respecitively. AICc model selection is based on lowest AICc value while AUC model selection is based on greatest AUC value. The horizontal axis corresponds to the cummulative number of axes included in the model of interest. A red dot corresponds to the AICc or AUC best model for that classification scheme.}
  \label{fig:sel}
\end{figure}
